Manuscript

### 2019-01-07 manuscript_analysis.Rmd
spearman/pearson overlap

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
```{r fig.height=5, fig.width=12}
crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
crispr_res_mut$corr <- 0
crispr_res_mut$Metric <- "Mutation Status"
crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
subset(crispr_res_mut, p < 0.05)

@@

@@

>>>>

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
crispr_signif_g2p_lineage_kable <- knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
```{r fig.height=5, fig.width=12}
crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
crispr_res_mut$corr <- 0
crispr_res_mut$Metric <- "Mutation Status"
crispr_res_mut$p_log10 <- -log10(as.numeric(crispr_res_mut$p))
subset(crispr_res_mut, p < 0.05)

@@

Mutation summaries for G2P gri comparisons:
```{r}
ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
ccle_mut_summ$Dataset <- "CCLE"

ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
ctrp_mut_summ$Dataset <- "CTRP"

gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
gdsc_mut_summ$Dataset <- "GDSC"

g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
```

@@

## Pearson/Spearman comparison

Compare significant Pearson and Spearman correlations:
```{r}
corr_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, Spearman_Pval_GE, InG2P, Dataset)
corr_summ_ge$Pearson_Pval_GE_log10 <- -log10(corr_summ_ge$Pearson_Pval_GE)
corr_summ_ge$Spearman_Pval_GE_log10 <- -log10(corr_summ_ge$Spearman_Pval_GE)
corr_summ_ge$Overlap_Status <- ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 & corr_summ_ge$Spearman_Pval_GE < 0.05, "Both", ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05, "Pearson", ifelse(corr_summ_ge$Spearman_Pval_GE < 0.05, "Spearman", NA)))
corr_summ_ge$Overlap_Status_Bonf <- ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 / nrow(corr_summ_ge) & corr_summ_ge$Spearman_Pval_GE < 0.05 / nrow(corr_summ_ge), "Both", ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 / nrow(corr_summ_ge), "Pearson", ifelse(corr_summ_ge$Spearman_Pval_GE < 0.05 / nrow(corr_summ_ge), "Spearman", NA)))
corr_summ_ge %>% count(Overlap_Status)
corr_summ_ge %>% count(Overlap_Status_Bonf)

corr_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, Spearman_Pval_CN, InG2P, Dataset)
corr_summ_cn$Pearson_Pval_CN_log10 <- -log10(corr_summ_cn$Pearson_Pval_CN)
corr_summ_cn$Spearman_Pval_CN_log10 <- -log10(corr_summ_cn$Spearman_Pval_CN)
corr_summ_cn$Overlap_Status <- ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 & corr_summ_cn$Spearman_Pval_CN < 0.05, "Both", ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05, "Pearson", ifelse(corr_summ_cn$Spearman_Pval_CN < 0.05, "Spearman", NA)))
corr_summ_cn$Overlap_Status_Bonf <- ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 / nrow(corr_summ_cn) & corr_summ_cn$Spearman_Pval_CN < 0.05 / nrow(corr_summ_cn), "Both", ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 / nrow(corr_summ_cn), "Pearson", ifelse(corr_summ_cn$Spearman_Pval_CN < 0.05 / nrow(corr_summ_cn), "Spearman", NA)))
corr_summ_cn %>% count(Overlap_Status)
corr_summ_cn %>% count(Overlap_Status_Bonf)
```
